Training a Gaming Agent on Brainwaves

### 2019-10-29 ErrP.tex
Varios cambios

Further work could be conducted in order to increase the complexity of the game to allow at least the possibility that the target position be dynamically changed.  In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.  Additionally, the classifier could be enhanced to recognize more effectively the Error Potential.

>>>>

Further work could be conducted in order to increase the complexity of the game to allow  the possibility that the target position be dynamically changed.  In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.  Additionally, the classifier could be enhanced to recognize more effectively the Error Potential.
